General exp analysis -- 4/18/2018

### 2018-11-02 resistingrhythm/analysis/paper_figures_v3.Rmd
Moved to un-norm rates in all figures

results200 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(rate_k - rate_ref), SD=sd(rate_k - rate_ref)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k - rate_ref, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="a.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
  # lims(y=c(0, 70)) +
  geom_hline(yintercept=0, size=0.2) +
  theme_classic() + 
  theme(plot.title = element_text(hjust = -.25, size=18, face="bold")) -> p3

@@

results201 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(rate_k - rate_ref), SD=sd(rate_k - rate_ref)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k - rate_ref, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="b.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
  # lims(y=c(-4, 4)) +
  geom_hline(yintercept=0, size=0.2) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p4

@@

results204 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(rate_k - rate_ref), SD=sd(rate_k - rate_ref)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k - rate_ref, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="darkgoldenrod3") +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.6, color="darkgoldenrod3") +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), 
                width=.15, size=0.2, color="darkgoldenrod3") +
  geom_hline(yintercept=0, size=0.2) +
  labs(title="c.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
  # lims(y=c(-3, 3)) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.4, size=18, face="bold")) -> p6

@@

tmp5 <- rbind(tmp3, tmp4)
tmp5 %>% 
  ggplot(aes(x=osc_mode, y=rate_k - rate_ref, color=osc_mode)) +
  geom_point(size=-1, aes(fill=osc_mode)) +
  geom_boxplot(notch = TRUE, width=0.4,  outlier.size=0.05, outlier.alpha=0.5, show.legend=FALSE) +
  labs(title="g.", y=expression(Delta*" rate (Hz)"), x="") +
  theme_classic() +
  geom_hline(yintercept=0, size=0.2) +
  # lims(y=c(-3, 3)) +
  scale_fill_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
  scale_color_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
  stat_compare_means(method="wilcox.test", label="p.signif", 
                     label.x=1.3, size=3, show.legend=FALSE) +
  guides(fill = guide_legend(override.aes = list(shape = 15, size = 7, alpha=0.8))) +
  theme(
    legend.position = c(0.15, 2),
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.5, "cm"),
    axis.text.x = element_text(angle = 70, hjust = 1),
    plot.title = element_text(hjust = -1.2, size=18, face="bold")) -> p7

@@

results202 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(rate_k - rate_ref), SD=sd(rate_k - rate_ref)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k - rate_ref, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="a.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
  # lims(y=c(0, 70)) +
  geom_hline(yintercept=0, size=0.2) +
  theme_classic() + 
  theme(plot.title = element_text(hjust = -.25, size=18, face="bold")) -> p3

@@

results203 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(rate_k - rate_ref), SD=sd(rate_k - rate_ref)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k - rate_ref, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="b.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
  # lims(y=c(-4, 4)) +
  geom_hline(yintercept=0, size=0.2) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p4

@@

results207 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(rate_k - rate_ref), SD=sd(rate_k - rate_ref)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k - rate_ref, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="darkgoldenrod3") +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.6, color="darkgoldenrod3") +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), 
                width=.15, size=0.2, color="darkgoldenrod3") +
  geom_hline(yintercept=0, size=0.2) +
  labs(title="c.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
  # lims(y=c(-3, 3)) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.4, size=18, face="bold")) -> p6

@@

# Rate
results218 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate, Ca_target) %>% 
  summarise(M=mean(rate_k - rate_ref), SD=sd(rate_k - rate_ref)) -> tmp2

tmp2 %>% 
ggplot(aes(x=osc_rate, y=M, color=factor(Ca_target, levels = c(0.026, 0.028, 0.03, 0.032, 0.034)))) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  geom_errorbar(aes(ymin=M - SD, ymax=M + SD), alpha=0.5, width=.1, size=0.4)  +
  labs(title="a", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
  geom_hline(yintercept=0, size=0.2) +
  scale_color_manual(
    values=c("plum1", "plum2", "black", "plum3", "plum4"), 
    name="Target [Ca]\n(mmolar)") +
  # lims(y=c(0, .01)) 
  # guides(col = guide_legend(ncol = 2)) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = -.5, size=18, face="bold"),
    legend.position = c(1.35, 0.0),
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.4, "cm")) -> p2

>>>>

results200 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="a.", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
  # lims(y=c(0, 70)) +
  geom_hline(yintercept=0, size=0.2) +
  theme_classic() + 
  theme(plot.title = element_text(hjust = -.25, size=18, face="bold")) -> p3

@@

results201 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="b.", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
  # lims(y=c(-4, 4)) +
  geom_hline(yintercept=0, size=0.2) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p4

@@

results204 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="darkgoldenrod3") +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.6, color="darkgoldenrod3") +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), 
                width=.15, size=0.2, color="darkgoldenrod3") +
  geom_hline(yintercept=0, size=0.2) +
  labs(title="c.", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
  # lims(y=c(-3, 3)) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.4, size=18, face="bold")) -> p6

@@

tmp5 <- rbind(tmp3, tmp4)
tmp5 %>% 
  ggplot(aes(x=osc_mode, y=rate_k - rate_ref, color=osc_mode)) +
  geom_point(size=-1, aes(fill=osc_mode)) +
  geom_boxplot(notch = TRUE, width=0.4,  outlier.size=0.05, outlier.alpha=0.5, show.legend=FALSE) +
  labs(title="g.", y="Norm. rate (Hz)", x="") +
  theme_classic() +
  geom_hline(yintercept=0, size=0.2) +
  # lims(y=c(-3, 3)) +
  scale_fill_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
  scale_color_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
  stat_compare_means(method="wilcox.test", label="p.signif", 
                     label.x=1.3, size=3, show.legend=FALSE) +
  guides(fill = guide_legend(override.aes = list(shape = 15, size = 7, alpha=0.8))) +
  theme(
    legend.position = c(0.15, 2),
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.5, "cm"),
    axis.text.x = element_text(angle = 70, hjust = 1),
    plot.title = element_text(hjust = -1.2, size=18, face="bold")) -> p7

@@

results202 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="a.", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
  # lims(y=c(0, 70)) +
  geom_hline(yintercept=0, size=0.2) +
  theme_classic() + 
  theme(plot.title = element_text(hjust = -.25, size=18, face="bold")) -> p3

@@

results203 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="b.", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
  # lims(y=c(-4, 4)) +
  geom_hline(yintercept=0, size=0.2) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p4

@@

results207 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="darkgoldenrod3") +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.6, color="darkgoldenrod3") +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), 
                width=.15, size=0.2, color="darkgoldenrod3") +
  geom_hline(yintercept=0, size=0.2) +
  labs(title="c.", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
  # lims(y=c(-3, 3)) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.4, size=18, face="bold")) -> p6

@@

# Rate
results218 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate, Ca_target) %>% 
  summarise(M=mean(rate_k), SD=sd(rate_k)) -> tmp2

tmp2 %>% 
ggplot(aes(x=osc_rate, y=M, color=factor(Ca_target, levels = c(0.026, 0.028, 0.03, 0.032, 0.034)))) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  geom_errorbar(aes(ymin=M - SD, ymax=M + SD), alpha=0.5, width=.1, size=0.4)  +
  labs(title="a", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
  geom_hline(yintercept=0, size=0.2) +
  scale_color_manual(
    values=c("plum1", "plum2", "black", "plum3", "plum4"), 
    name="Target [Ca]\n(mmolar)") +
  # lims(y=c(0, .01)) 
  # guides(col = guide_legend(ncol = 2)) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = -.5, size=18, face="bold"),
    legend.position = c(1.35, 0.0),
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.4, "cm")) -> p2
